Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Harmonize the dimension abbreviation

Note that $h$ is only well-defined if the bow of $M$ is oriented on the positive $z$ axis.
Therefore, a 2d rotation is first applied to the vertices $\mathbf x$ before applying $h$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Height field}
At this point, equations are still too complex to be used in real-time, especially in terms of dimension:
it seems inconceivable to solve them at large scale in 3d.
Therefore, to reduce their dimensions it is assumed that the surface geometry is described by a height field, as follows:
\begin{equation}
	y = h(\mathbf x, t).
\end{equation}

>>>>

Note that $h$ is only well-defined if the bow of $M$ is oriented on the positive $z$ axis.
Therefore, a 2D rotation is first applied to the vertices $\mathbf x$ before applying $h$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Height field}
At this point, equations are still too complex to be used in real-time, especially in terms of dimension:
it seems inconceivable to solve them at large scale in 3D.
Therefore, to reduce their dimensions it is assumed that the surface geometry is described by a height field, as follows:
\begin{equation}
	y = h(\mathbf x, t).
\end{equation}
